Prediction of 2024 US election ...

### 2024-11-03 paper/paper.qmd
added the idealized survey

```{r}
#| label: fig-avg-pct-methodology
#| fig-cap: Most Metholodgies Do Not Bias Towards a Candidate
#| echo: false
#| warning: false
#| 
cleaned_data <- cleaned_data %>% mutate(candidate_name =
  if_else(!(candidate_name %in% c("Kamala Harris", "Donald Trump")), "Other", candidate_name))

@@

# Overview of American Electon System

# Brief Description of American Federal Goverment

@@

## What is the Electoral College {#sec-electoral-college}

@@

state_colors <- c(
  alabama = dark_red,
  arizona = purple,
  arkansas = dark_red,
  california = dark_blue,
  colorado = dark_blue,
  connecticut = dark_blue,
  delaware = dark_blue,
  `district of columbia` = dark_blue,
  florida = light_blue,
  georgia = purple,
  idaho = dark_red,
  illinois = dark_blue,
  indiana = dark_red,
  iowa = light_red,
  kansas = dark_red,
  kentucky = dark_red,
  louisiana = dark_red,
  maine = "gray",
  maryland = dark_blue,
  massachusetts = dark_blue,
  michigan = purple,
  minnesota = light_blue,
  mississippi = dark_red,
  missouri = dark_red,
  montana = dark_red,
  nebraska = "gray",
  nevada = purple,
  `new hampshire` = light_blue,
  `new jersey` = dark_blue,
  `new mexico` = light_blue,
  `new york` = dark_blue,
  `north carolina` = purple,
  `north dakota` = dark_red,
  ohio = light_red,
  oklahoma = dark_red,
  oregon = dark_blue,
  pennsylvania = purple,
  `rhode island` = dark_blue,
  `south carolina` = dark_red,
  `south dakota` = dark_red,
  tennessee = dark_red,
  texas = light_red,
  utah = dark_red,
  vermont = dark_blue,
  virginia = light_blue,
  washington = dark_blue,
  `west virginia` = dark_red,
  wisconsin = purple,
  wyoming = dark_red
)

@@

# States Poll Count

@@

>>>>

```{r}
#| label: fig-avg-pct-methodology
#| fig-cap: Polls with more Methodologies have Less Variability.
#| echo: false
#| warning: false
#| 
cleaned_data <- cleaned_data %>% mutate(candidate_name =
  if_else(!(candidate_name %in% c("Kamala Harris", "Donald Trump")), "Other", candidate_name))

@@

## Overview of American Electon System

## Brief Description of American Federal Goverment

@@

### What is the Electoral College {#sec-electoral-college}

@@

state_colors <- c(
  alabama = dark_red,
  arizona = purple,
  arkansas = dark_red,
  california = dark_blue,
  colorado = dark_blue,
  connecticut = dark_blue,
  delaware = dark_blue,
  `district of columbia` = dark_blue,
  florida = light_red,
  georgia = purple,
  idaho = dark_red,
  illinois = dark_blue,
  indiana = dark_red,
  iowa = light_red,
  kansas = dark_red,
  kentucky = dark_red,
  louisiana = dark_red,
  maine = "gray",
  maryland = dark_blue,
  massachusetts = dark_blue,
  michigan = purple,
  minnesota = light_blue,
  mississippi = dark_red,
  missouri = dark_red,
  montana = dark_red,
  nebraska = "gray",
  nevada = purple,
  `new hampshire` = light_blue,
  `new jersey` = dark_blue,
  `new mexico` = light_blue,
  `new york` = dark_blue,
  `north carolina` = purple,
  `north dakota` = dark_red,
  ohio = light_red,
  oklahoma = dark_red,
  oregon = dark_blue,
  pennsylvania = purple,
  `rhode island` = dark_blue,
  `south carolina` = dark_red,
  `south dakota` = dark_red,
  tennessee = dark_red,
  texas = light_red,
  utah = dark_red,
  vermont = dark_blue,
  virginia = light_blue,
  washington = dark_blue,
  `west virginia` = dark_red,
  wisconsin = purple,
  wyoming = dark_red
)

@@

## States Poll Count

@@

## The Ideal Survey

### Objective

The research team has developed a survey and distribution methodology with a hypothetical budget of $100,000. This objective is to create a polling system that accurately predicts the 2024 United States Election.

### Sampling Frame

Given the monetary constraint, the team's first decision is to mostly include swing states and districts. These are Nevada, Arizona, Wisconsin, Michigan, Pennsylvania, North Carolina, and Georgia. Swing states are the primary focus of the poll because they disproportionately affect the outcome of the election based on the explanation in @sec-PLACEHOLDER. However, the poll will also include Texas, Florida, and Minnesota, Nebraska District 2, and Maine District 2, as they have the potential to one by either party but are not as likely to change as the previously mentioned swing states. Nevertheless, it is important to note that to save costs, the team will focus on polling true swing states compared to Texas, Florida and Minnesota.

### Survey Sending Process

The team will then find and use multiple databases, such as @uspostalserviceresidentialaddressfile, to find addresses, telephones, and emails of potential voters in those states. According to @pewresearch, gathering this information reduces non-response and selection bias, as the team can contact the same individual through multiple mediums. Moreover, certain demographics may prefer specific communication forms; for instance, the elderly may prefer phone or paper mail polls over text or email. Additionally, to encourage individuals to complete the survey, one in every 50 participants will have a chance at winning $20.

### Sampling Methodology

Each state will have its own poll, but the polling methodology and the survey given will remain the same. Specifically, the polls will use stratified random sampling to make sure that participants reflect each state's counties in proportion to their population sizes. Ideally, the stratification would also ensure race, gender, age, and other socioeconomic factors are also accounted for. However, these factors are almost impossible to determine while sending the survey. Therefore, the research team decided to ask demographic questions directly inside the survey. After data collection, the team will weigh data based on demographics. For example, if a certain county has a 30% black population (this statistic will be determined from the US census), but only 15% of the survey participants are black, then the pollsters may decide to count each black participant's responses twice.

Furthermore, the team will aim to sample approximately 1,000 people from each true swing state. This sample size is large enough to provide reliable conclusions but not so large that it resembles sampling with replacement. For true swing states, the team aims to survey 1,000 individuals. However, if the final sample size falls short of this target, it is not considered a significant issue.

### Survey Implementation & Question Creation

The team's ideal survey will be made using @qualtrics. It will attempt to ensure four things: no leading questions, no question order bias, no answer order bias, and the survey should identify non-engaged participants. To identify participants who are not engaged, the research team has decided to add a worthless question. This question is extremely simple and clearly has one correct answer. Therefore, if a participant selects the wrong answer, they most likely are not engaged with the survey and their responses should be removed from the final data. An example of this is question number 7.

Order bias occurs when the sequence of questions subconsciously influences participants' responses. To prevent this, many questions should be randomized upon entry to the survey. However, some questions must follow a specific order, such as question 11, while others like questions 1-4 can be randomized. The team's hypothetical survey has not implemented this feature, though it is available with the @qualtrics paid plan.

Answer bias, like order bias, occurs when the order of answer choices influences participants' selections, with the first option often chosen more frequently. To prevent this, answer choices should be randomized upon survey entry. Questions 8 & 9 could benefit from this. Likewise, the team's hypothetical survey has not implemented this feature, but it is available in the @qualtrics paid plan.

A leading question occurs when a question is written in a way that suggests the user to give a certain answer. For example, "given that children are the future of our country, should we invest more money in their education". To prevent this, the researchers have ensured questions are written in a style where no unnecessary details or opinions are added.

### Survey Questions

Click this (link)[https://qualtricsxm7d2hxss4j.qualtrics.com/jfe/form/SV_1Tu3PT2eUEa1Op8] for the @qualtrics survey.

List of all of the questions:

1. Select your race(s) (racial options where chosen based on @whitehouseracialoptions-PLACEHOLDER)
   - White
   - Black or African American 
   - American Indian or Alaska Native 
   - Native Hawaiian or Pacific Islander 
   - Middle Eastern or North African
   - Asian 
   - Other 
   - Prefer not to answer

2. Please select your gender 
   - Male 
   - Female 
   - Non-binary 
   - Prefer not to say

3. Please enter your age (in numbers) 
  - This is a text input field. Please note that this field has the auto-validation feature set to numbers in @qualtrics. As a result, participants can only input numbers in this field and are alert if they have not.

4. Please select the highest degree of education you have obtained
   - GED Certificate 
   - High School Diploma 
   - Undergraduate Degree 
   - Graduate Degree (Masters/Phd) 
   - None 
   - Other
   - Prefer not to answer

5. Are you a registered voter for the 2024 United States Presidential Election? 
   - Yes 
   - No

6. Place yourself on the political spectrum 
   - Far Left 
   - Center Left 
   - Center 
   - Center Right 
   - Far Right

7. Can pigs fly? 
   - Yes 
   - Maybe
   - No 
   - Prefer Not To Say

8. What political party have you registered with? 
   - Republicans 
   - Democrats 
   - Green Party 
   - Libertarian 
   - Other
   - Independent (unregistered)

9. Who will you vote for in the 2024 presidential election? 
   - Democrat - Kamala Harris 
   - Republican - Donald Trump 
   - Green Party - Gill Stein 
   - Libertarian - Chase Oliver 
   - Other
   - Will not vote

### Potential Problems with the Methodology And Polls

While the team's methodology and survey creates a robust system, there are potential issues. The reliance of weighting results based on a candidate's demographics can lead to error propagation. For instance, if a certain racial demographic population is only captured limitedly and that limited sample is far from representative, a few individuals in the population can have a large impact on the polls prediction of what candidate will win the state. There is also a selection bias in terms of the monetary reward. Potentially, people who like monetary rewards could be more likely to engage in the survey and could therefore exhibit certain voting or demographic characteristics that create an unrepresentative sample.
